\documentclass{article}        % Your input file must contain these two lines
\begin{document}
\textbf{Heinz H.\ Bauschke}
is a Professor of Mathematics
at the University of British Columbia, Kelowna and
a \emph{Canada Research Chair (Tier 2)} in
Convex Analysis and Optimization.

He was born in Frankfurt, where
he received his ``Diplom-Mathematiker (mit Auszeichnung)''
from Goethe Universit\"at  in 1990.
He defended his PhD thesis in Mathematics at Simon Fraser University
in 1996, and was awarded the \emph{Governor General's Gold Medal}
for his graduate work.
After an NSERC Postdoctoral Fellowship spent
at the University of Waterloo, at the Pennsylvania State University,
and at the University of California at Santa Barbara,
Dr.~Bauschke
became College Professor at Okanagan University College in 1998.
He was also Principal Researcher for Workfire and Packeteer, where
his work on JPEG image compression led to a U.S.~patent.
He joined the University of Guelph in 2001, and he returned
to Kelowna in 2005, when Okanagan University College turned
into the University of British Columbia, Okanagan campus in Kelowna
(UBCO).

Dr.\ Bauschke has authored or co-authored more than 80 papers in
Analysis and Optimization.
Jointly with Dr.\ Patrick Combettes, he has just completed and
published the 450+ pages monograph \emph{Convex Analysis and Monotone
Operator Theory in Hilbert Spaces} with Springer Verlag.
He has also co-edited the book
\emph{Fixed-Point Algorithms for Inverse Problems in Science
and Enginnering}, which appeared in 2011 in the
Springer series \emph{Optimization and Its Application}.
His work has been cited more than 3000 times\footnote{Source:
AMS MathSciNet on September 7, 2011}.
In 2009, he became UBCO's first \emph{Researcher of the Year}.
\end{document}
